Modelling last glacial cycle ice dynamics in the Alps

### 2017-08-08 articles/cycle/alps-cycle.tex
Add warm ice cover less than 1ka on trimlines fig.
Use max elev. age in trimline fig, update caption.

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Modelled age of maximum ice thickness (colour) and maximum
        ice surface elevation (200\,m contours) above trimline locations
        \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley.
        \textbf{(b)} Modelled maximum ice thickness against observed trimline
        elevations \citep[Table~1]{Kelly.etal.2004}.
        \textbf{(c)} Histogram of modelled maximum ice thickness above trimline
        locations (500\,m bands). The average maximum ice thickness above the
        trimline is 979\,m.
        \todo{Add cold ice areas or so. Use max
              surface elevation age as in Fig.~\ref{fig:timing}.}}
      \label{fig:trimlines}
    \end{figure}

>>>>

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Modelled maximum ice thickness against observed trimline
        elevations \citep[Table~1]{Kelly.etal.2004}.
        \textbf{(b)} Histogram of modelled maximum ice thickness above trimline
        locations (500\,m bands). The average maximum ice thickness above the
        trimline is 979\,m.}
        \textbf{(c)} Modelled age of maximum ice thickness (colour) and maximum
        ice surface elevation (200\,m contours) above trimline locations
        \citep[Table~1]{Kelly.etal.2004} in the upper Rhone valley. Hatches
        mark glaciated areas with less than 1\,ka temperate ice cover during
        MIS~2 (29--14\,ka).
      \label{fig:trimlines}
    \end{figure}
